A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-06-28 paper/elsarticle/elsarticle-template.tex
Update elsarticle-template.tex

The hardware setup employed in this work comprised a Panasonic PT-RZ660BE projector with a steerable mirror system manufactured by Dynamic Projection Institute. In addition, we used a Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The setup was mounted on the ceiling of the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. The floorspace used for our experiments measured dimensions of ca.\ X~m~$\times$~Y~m; the projector was mounted at approximately the center of this space, at a height of ca.\ XX m.

>>>>

The hardware setup employed in this work comprised a Panasonic PT-RZ660BE projector with a steerable mirror system manufactured by Dynamic Projection Institute. In addition, we used a Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The setup was mounted on the ceiling of the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. The floorspace used for our experiments measured dimensions of ca.\ X~m~$\times$~Y~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.
